Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-04-30 ms.Rmd
Fixed all the main MS so that all contrasts, p-values etc are using robust variance esatimatos to corrects SEs and p-values, also using Bonferroni corrections as a super conservative path

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Predator_IDs <- Predator %>% filter(!is.na(Predator), !is.na(Population)) # filter out misssing data
    robust_PredatorAC <- coef_test(PredatorAC, cluster = Predator_IDs$ID, vcov = "CR2")

@@

    # Support for an interaction between predator type and population in the chromatic realm. Planned comparisons. First re-fit model
      Predator$pred_pop <- with(Predator, interaction(Predator, Population))
    PredatorCC_pred_pop <- lmer(dS ~ pred_pop + (1|ID), data = Predator) 
    summary(PredatorCC_pred_pop)

    # Conduct hypothesis tests of interest
    hypthesis_test <- glht(PredatorCC_pred_pop, df = 101-1, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pred_pop = c("snake.Hawaii - snake.Kenya = 0",
                                       "bird.Hawaii  - bird.Kenya = 0",
                                       "snake.Hawaii - bird.Hawaii = 0",
                                    "snake.Kenya  - bird.Kenya = 0")))
    # Get the contrasts, and statistical data for these plannned comparions.
      summary(hypthesis_test)
      CI_hyp_test <- as.data.frame(confint(hypthesis_test)$confint)

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Predator_IDs <- Predator %>% filter(!is.na(Predator), !is.na(Population)) # filter out misssing data
    robust_PredatorCC <- coef_test(PredatorCC, cluster = Predator_IDs$ID, vcov = "CR2")

@@

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
  robust_localAdapt <- clubSandwich::coef_test(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

  # Planned contrast. Fit the model in a slightly different way
  DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
  DisplayBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = DisplayBgrd)

  # df to get t-distribution, use number of lizards not data points
  hypthesis_test_preppop <- glht(DisplayBgrd_pop_back, df = 69-1, 
               linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

  # Grab contrast stats for paper
  summary(hypthesis_test_preppop)
  p_displ_AC <- as.numeric(summary(hypthesis_test_preppop)$test$pvalues)
   CI_dis_AC <- as.data.frame(confint(hypthesis_test_preppop)$confint)
##########
# Chromatic Contrast - dS
##########

@@

    # Conduct hypothesis test, df to get t-distribution, use number of lizards not data points
      hypthesis_test_preppop_CC <- glht(DisplayBgrd_pop_backCC, df = 69-1, 
             linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

    # Grab the statistics for the paper
      summary(hypthesis_test_preppop_CC)
      p_displ_CC <- as.numeric(summary(hypthesis_test_preppop_CC)$test$pvalues)
      CI_Disp_CC <- as.data.frame(confint(hypthesis_test_preppop_CC)$confint)

@@

  # Hypothesis tests
      hypthesis_test_preppopCourtship <- glht(CourtshipBgrd_pop_back, df = 69-1, 
                                        # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

      summary(hypthesis_test_preppopCourtship)

  # Grab the stats for paper
      p_courtship_AC <- as.numeric(summary(hypthesis_test_preppopCourtship)$test$pvalues)
CI_AC_Courtship <- data.frame(confint(hypthesis_test_preppopCourtship)$confint)

@@

  # Specific planned comparisons, # df to get t-distribution, use number of lizards not data points
      hypthesis_test_preppopCourtshipCC <- glht(CourtshipBgrd_pop_backCC, df = 69-1, 
             linfct = mcp(pop_back = c("Hawaii.Kenya - Hawaii.Hawaii = 0")))

  # Grab summary stats for paper
    summary(hypthesis_test_preppopCourtshipCC)
    p_courtship_CC <- as.numeric(summary(hypthesis_test_preppopCourtshipCC)$test$pvalues)
    CI_CC_Courtship <- data.frame(confint(hypthesis_test_preppopCourtshipCC)$confint)
```

@@

As a consequence of signal release, sexual signals are expected to be more easily detected by predators (i.e., snakes and birds) in Hawaii. Differential predation pressure resulting from snake and bird predation varying would also result in populations varying in their conspicuousness to different predators.  In support of these predictions, Hawaiian chameleons were significantly more conspicous to both snake and bird predators (figure 1b & c; Achromatic Contrast: ($dl$); $F_{`r anova_predators$NumDF[2]`,`r anova_predators$DenDF[2]`}$ = `r anova_predators[5][2,]`, p = `r p_value(anova_predators[6][2,])`). Differences in chromatic contrast between populations, however,  depended on the predator (significant predator by population interaction: $F_{`r anova_predators_interCC$NumDF[3]`,`r anova_predators_interCC$DenDF[3]`}$ = `r anova_predators_interCC[5][3,]`, p = `r p_value(anova_predators_interCC[6][3,])`). Interestingly, Kenyan and Hawaiian lizards were equally detectable by snakes, but Kenyan chameleons were significantly more cryptic from birds compared to Hawaiian chamleons (figure 1c; Snakes (Hawaii-Kenya): `r CI_hyp_test[1,1]`, 95% CI = `r CI_hyp_test[1,2]` to `r CI_hyp_test[1,3]`, p = 1; Birds (Hawaii-Kenya): `r CI_hyp_test[2,1]`, 95% CI = `r CI_hyp_test[2,2]` to `r CI_hyp_test[2,3]`, p = < 0.001).

>>>>

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Predator_IDs <- Predator %>% filter(!is.na(Predator), !is.na(Population)) # filter out misssing data
       robust_PredatorAC <- coef_test(PredatorAC, cluster = Predator_IDs$ID, vcov = "CR2")
    robust_PredatorAC_CI <-  conf_int(PredatorAC, cluster = Predator_IDs$ID, vcov = "CR2")

@@

    # Support for an interaction between predator type and population in the chromatic realm. Planned comparisons. First re-fit model
      Predator$pred_pop <- with(Predator, interaction(Predator, Population))
    PredatorCC_pred_pop <- lmer(dS ~ -1 + pred_pop + (1|ID), data = Predator) 
    summary(PredatorCC_pred_pop)

    # Fit RVE, we want contrast effects because annoyingly RVE doesn't provide them so will relevel to get them in the context of RVE

    # Model allows us to get bird in Hwaii compared to bird in Kenya (contrast 3)
      PredatorCC_pred_pop1 <- lmer(dS ~  pred_pop + (1|ID), data = Predator) 
      summary(PredatorCC_pred_pop1)
      PredatorCC_pred_pop2 <- lmer(dS ~  relevel(pred_pop, ref = "snake.Hawaii") + (1|ID), data = Predator) 
      summary(PredatorCC_pred_pop2)

      # Fit the models so we get the estimate and corrected robust standard error for the contrasts we want to make
      robust_PredatorCC_pred_pop1 <- conf_int(PredatorCC_pred_pop1, cluster = Predator$ID, vcov="CR2")
      robust_PredatorCC_pred_pop2 <- conf_int(PredatorCC_pred_pop2, cluster = Predator$ID, vcov="CR2")

     # Contrasts hypothesis tests, but use RVE 
    result_pred <- Wald_test(PredatorCC_pred_pop, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
    result_pred$p_val_bonfer <- sapply(p.adjust(result_pred$p_val, "bonferroni"), function(x) p_value(x))

    # Get the contrasts and Wald stats for comparions
     CI_hyp_test <- data.frame(
              comparison = c("Snake (Hawaii-Kenya)", "Birds (Hawaii-Kenya)"), 
                Estimate = c(robust_PredatorCC_pred_pop2[4,1], robust_PredatorCC_pred_pop1[3, 1]),
                lwr = c(robust_PredatorCC_pred_pop2[4,4], robust_PredatorCC_pred_pop1[3, 4]),
                upr = c(robust_PredatorCC_pred_pop2[4,5], robust_PredatorCC_pred_pop1[3, 5]),
              Fstat = c(result_pred[5,3], result_pred[2,3]),
              df = c(result_pred[5,5], result_pred[2,5]),
              p_val = c(result_pred[5,7], result_pred[2,7]),
              p_bonf = c(result_pred[5,8], result_pred[2,8]))

@@

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
  robust_localAdapt <- clubSandwich::conf_int(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

  # Planned contrast. Fit the model in a slightly different way
  DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
  DisplayBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = DisplayBgrd) 
  summary(DisplayBgrd_pop_back)

  robust_DisplayBgrd_pop_back <- clubSandwich::conf_int(DisplayBgrd_pop_back, cluster = DisplayBgrd$ID, vcov =  "CR2")

  # Contrasts hypothesis tests, but use RVE 
    result_DisplayBgrd_pop_back <- Wald_test(DisplayBgrd_pop_back, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
    result_DisplayBgrd_pop_back$p_val_bonfer <- sapply(p.adjust(result_DisplayBgrd_pop_back$p_val, "bonferroni"), function(x) p_value(x))

  # Grab contrasts that we need from the robust esatimtes
  p_displ_AC <- as.numeric(result_DisplayBgrd_pop_back[2,8])
   CI_dis_AC <- data.frame(Estimate=robust_DisplayBgrd_pop_back$beta[3],
                           lwr = robust_DisplayBgrd_pop_back$CI_L[3],
                           upr = robust_DisplayBgrd_pop_back$CI_U[3])

##########
# Chromatic Contrast - dS
##########

@@

    # Fit Robust model
    robust_DisplayBgrd_pop_backCC <- clubSandwich::conf_int(DisplayBgrd_pop_backCC, cluster = DisplayBgrd$ID, vcov =  "CR2")

    # Contrasts hypothesis tests, but use RVE 
      result_DisplayBgrd_pop_backCC <- Wald_test(DisplayBgrd_pop_backCC, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
      result_DisplayBgrd_pop_backCC$p_val_bonfer <- sapply(p.adjust(result_DisplayBgrd_pop_back$p_val, "bonferroni"), function(x) p_value(x))

    # Grab contrasts that we need from the robust esatimtes
      p_displ_CC <- result_DisplayBgrd_pop_backCC[2,8]
       CI_Disp_CC <- data.frame(Estimate=robust_DisplayBgrd_pop_backCC$beta[3],
                               lwr = robust_DisplayBgrd_pop_backCC$CI_L[3],
                               upr = robust_DisplayBgrd_pop_backCC$CI_U[3])

@@

   # Fit Robust model
    robust_CourtshipBgrd_pop_back <- clubSandwich::conf_int(CourtshipBgrd_pop_back, cluster = CourtshipBgrd$ID, vcov =  "CR2")

    # Contrasts hypothesis tests, but use RVE 
      result_CourtshipBgrd_pop_back <- Wald_test(CourtshipBgrd_pop_back, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
      result_CourtshipBgrd_pop_back$p_val_bonfer <- sapply(p.adjust(result_CourtshipBgrd_pop_back$p_val, "bonferroni"), function(x) p_value(x))

    # Grab contrasts that we need from the robust esatimtes
      p_courtship_AC <- result_CourtshipBgrd_pop_back[2,8]
       CI_AC_Courtship <- data.frame(Estimate=robust_CourtshipBgrd_pop_back$beta[3],
                               lwr = robust_CourtshipBgrd_pop_back$CI_L[3],
                               upr = robust_CourtshipBgrd_pop_back$CI_U[3])

@@

     # Fit Robust model
    robust_CourtshipBgrd_pop_backCC <- clubSandwich::conf_int(CourtshipBgrd_pop_backCC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

    # Contrasts hypothesis tests, but use RVE 
      result_CourtshipBgrd_pop_backCC <- Wald_test(CourtshipBgrd_pop_backCC, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
      result_CourtshipBgrd_pop_backCC$p_val_bonfer <- sapply(p.adjust(result_CourtshipBgrd_pop_backCC$p_val, "bonferroni"), function(x) p_value(x))

    # Grab contrasts that we need from the robust esatimtes
      p_courtship_CC <- result_CourtshipBgrd_pop_backCC[2,8]
       CI_CC_Courtship <- data.frame(Estimate=robust_CourtshipBgrd_pop_backCC$beta[3],
                               lwr = robust_CourtshipBgrd_pop_backCC$CI_L[3],
                               upr = robust_CourtshipBgrd_pop_backCC$CI_U[3])

@@

As a consequence of signal release, sexual signals are expected to be more easily detected by predators (i.e., snakes and birds) in Hawaii. Differential predation pressure resulting from snake and bird predation varying would also result in populations varying in their conspicuousness to different predators.  In support of these predictions, Hawaiian chameleons were significantly more conspicous to both snake and bird predators (figure 1b & c; Achromatic Contrast: ($dl$); $F_{`r anova_predators$NumDF[2]`,`r anova_predators$DenDF[2]`}$ = `r anova_predators[5][2,]`, p = `r p_value(anova_predators[6][2,])`). Differences in chromatic contrast between populations, however,  depended on the predator (significant predator by population interaction: $F_{`r anova_predators_interCC$NumDF[3]`,`r anova_predators_interCC$DenDF[3]`}$ = `r anova_predators_interCC[5][3,]`, p = `r p_value(anova_predators_interCC[6][3,])`). Interestingly, Kenyan and Hawaiian lizards were equally detectable by snakes, but Kenyan chameleons were significantly more cryptic from birds compared to Hawaiian chamleons (figure 1c; Snakes (Hawaii-Kenya): `r CI_hyp_test[1,2]`, 95% CI = `r CI_hyp_test[1,3]` to `r CI_hyp_test[1,4]`, p = 1; Birds (Hawaii-Kenya): `r CI_hyp_test[2,2]`, 95% CI = `r CI_hyp_test[2,3]` to `r CI_hyp_test[2,4]`, p = `r CI_hyp_test[2,8]`).
